Regime transition identification for water utilization of river basin

### 2020-10-25 tex/main/manuscript.tex
polished by wu's suggestion v2

%tag 摘要
\begin{abstract}
	\label{abstract}
	% For water utilization as blood that sustains social developments, humans have harnessed basins, modified river cycles and triggered a range of regime shifts all around the world.
	For sustaining socio-economic development, human have harnessed large rivers and triggered a range of regime shifts at a basin scale all around the world. 
	Detecting these abrupt reorganizations of structure and function is crucial for understanding changes of human-water system. 
	Here, considering three main dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts. 
	By applying this index to the Yellow River Basin, China, it suggests that there were two regime shifts over half a century, whose drivers were economic growths, managements and efficiency improvement.
	Differ from previous onefold descriptions, IWRU captures various considerations intertwined in water utilization, based on which we proposed a transition framework in interpreting associated changes.
	By identifying and predicting widespread dilemmas in transition of water utilization, this framework can be a useful guideline for big river basins to develop in a coordinated way.
\end{abstract}

@@

\begin{figure*}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		\textbf{Transition framework of water utilization.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. 
		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
		However, as their ecological services generated through the socio-economic path, water resource are non-provisioning. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:summary}
\end{figure*}

% 上述过渡过程与稳态转换的关联可能是普遍的
The links between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic processes are gradually dominating human-water systems in most river basins.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework, which conceptualizes a general trajectory towards regional socio-economic dominating water utilization stage by stage (Figure~\ref{fig:summary}).
% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。

>>>>

%tag 摘要
\begin{abstract}
	\label{abstract}
	% For water utilization as blood that sustains social developments, humans have harnessed basins, modified river cycles and triggered a range of regime shifts all around the world.
	For sustaining socio-economic development, human have harnessed large rivers and triggered a range of regime shifts at a basin scale all around the world. 
	Detecting these abrupt reorganizations of structure and function is critical to successful future river basin management. 
	Here, considering three main dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts. 
	By applying this index to the Yellow River Basin, China, it suggests that there were two regime shifts over half a century, whose drivers were economic growths, managements and efficiency improvement.
	Differ from previous onefold descriptions, IWRU captures various considerations intertwined in water utilization, based on which we proposed a transition framework in interpreting associated changes.
	By identifying and predicting widespread dilemmas in transition of water utilization, this framework can be a useful guideline for big river basins to develop in a coordinated way.
\end{abstract}

@@

\begin{figure*}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		\textbf{Transition framework of water utilization.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. 
		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:summary}
\end{figure*}

% 上述过渡过程与稳态转换的关联可能是普遍的
The links between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic processes are gradually dominating human-water systems in most river basins.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework, which conceptualizes a general trajectory towards regional socio-economic dominating water utilization stage by stage.
% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
In the framework, provisioning water utilization (agriculture, domestic or livestock) are dominated at the primal phase and social processes take over dominating with growths of industry and services in the followed phases, with coordinated considerations of water utilization over the whole basin (Figure~\ref{fig:summary}).
